%
% file: localoperator.tex
% author: Victor Brena
% description: Briefly describes properties of the local operator.
%

\chapter{Contact and Support Information}
\label{app:app01}

\section*{Contact Information}
\begin{center}
\begin{tabular}{ c c c }	
\textbf{Name} & \textbf{Title} & \textbf{E\-mail} \\
Samantha Goldberg & Local Activities Coordinator & local\_activities@acm.org \\
Donna Cappo & Director, Office of SIG Services & cappo@acm.org \\
Russell Harris & Director of Finance & rharris@acm.org \\
Wayne Graves & Director of IS & support@acm.org   
\end{tabular}
\end{center}

\section*{Membership Promotion}
The headquarters office can help chapters planning ACM membership drives by providing the following:
\begin{itemize}
	\item Membership Applications
    \item Membership Brochures
	\item Publications Catalogs
	\item SIG Reference Guides
	\item ACM plastic bags for use in conferences, etc.
	\item Samples of ACM major publications and SIG newsletters
	\item ACM logo in camera-ready or electronic format
\end{itemize}

\section*{Publicity}
ACM headquarters would welcome the opportunity to publicize newsworthy events. MemberNet is a quarterly newsletter of ACM news, which is sent to all ACM members along with their issues of Communications of the ACM. Items of wide interest may be submitted for publication by contacting the Local Activities Coordinator.

Pressure-sensitive labels for ACM members in your geographic are can also be obtained by contacting the Local Activities Coordinator.

Some examples of newsworthy items include the following:
\begin{itemize}
	\item Important joint meetings with other societies
	\item Renowned speakers
	\item Local conferences/workshops/seminars
	\item Special awards or recognition
	\item Scholarships
	\item Contests/competitions
\end{itemize}

\section*{Recognition of Service Certificates}
Recognition of service certificates for outgoing ACM Professional chairpersons who have served at least one year in office will be issued free of charge upon written request. Certificates for other officers will be issued on a cost recovery basis. The cost is \$19.00 per certificate. These certificates are signed by the ACM President and Secretary. Send your request to local\_activites@acm.org.

\section*{Depository for Bylaws}
Headquarters coordinates the initial processing of petitions and bylaws for new chapters as well as bylaw amendments with the Membership Services Board, and issues a Certificate of Charter when a chapter is chartered. Copies of each chapter's bylaws are kept on file at Headquarters, and are available upon request.

\section*{Financial Guidance}
Each chapter is required to submit a statement of Cash Receipts and Disbursements every year. The Local Activities Coordinator can answer most general questions about the form, as well as other basic questions regarding financial management. All inquiries from the IRS to the chapter should be directed to the ACM Director of Finance. Any chapter desiring to solicit funds of more than \$5,000 cash or equivalent goods or services from a single source must obtain in advance the approval of ACM's Chief Operations Officer. Solicitations of donations of small magnitude for a specific goal of a specified time do not require approval.


\