%
% file: app0B.tex
% author: Wesley Hoffman
% description: ACM SIG Registration
%

\chapter{ACM SIG Registration}
\label{app:app02}

\section{Registering a SIG}
\label{sec:sec01}

\textbf{Step 1:}  Enter chapter name, chapter email address, chapter type, and chapter sub-type at http://campus.acm.org/public/chapters/AutoChap/.
\\
\\
\textbf{Step 2:}  Enter the names of three individuals to serve as Chair, Vice Chair and Secretary/Treasurer. These individuals must be ACM Student Members. In addition, a Faculty Sponsor with an ACM Professional Membership and relevant SIG Membership is required.
\\
\\
\textbf{SIGGRAPH Chapter:}  Enter the names of four individuals to serve as Chair, Vice Chair, Secretary and Treasurer. These individuals must be ACM Student Members and Student SIGGRAPH Members. In addition, a Faculty Sponsor with an ACM Professional Membership and SIGGRAPH Membership is required.
\\
\\
\textbf{Step 3:}  Enter chapter contact information (postal address and phone number).
\\
\\
\textbf{Step 4:}  Enter the names of at least ten (10) individuals willing to carry out the chapter's mission and participate in activities.  A CSV file (comma-separated values) containing the last name, middle initial, first name, and email addresses of these members will be required through the automated chartering application.

\begin{flushright}
Example: "Doe","John","johndoe@domain.com"
\end{flushright}

You may enter each member name individually.
\\
Once the completed application is submitted, SIG Chapter's require additional approval by volunteers; this secondary approval process will take up to 2 weeks. You will be notified via email on the approval of your chapter.
\\
\textbf{Note:}
\\
\textbf{FOR UNITED STATES CHAPTERS:}  The IRS requires chapters operating in the United States to have an Employer Identification Number (EIN). The EIN will serve as proof of a chapter's nonprofit status and allow ACM to include the chapter in our annual group filing with the IRS. ACM will request an EIN on your behalf which you will receive upon chartering.
