%
% File: chap03.tex
% Author: Wesley Hoffman
% Description: ACM Bylaws
%
\let\textcircled=\pgftextcircled
\chapter{Bylaws}
\label{chap:bylaws}

\initial{S}tudent chapters should not change the bylaws in any way, with the exception of adding clauses mandated by the university, such as a non-discrimination clause or any clause addressing the receipt and disbursement of funds given to the chapter by the university. Any other changes to this bylaws template will not be accepted.

%======================
\section{Chapter Bylaws}
\label{sec:sec01}

\section*{Article I: Name}
\begin{enumerate}
	\item This organization shall be called the University of Kansas at Lawrence Student Chapter. In these Bylaws it is referred to as the Chapter; the Association for Computing Machinery is referred to as the ACM.
\end{enumerate}

\section*{Article II: Purpose}
\begin{enumerate}
	\item The Chapter is organized and will be operated exclusively for educational and scientific purposes to promote the following:
   \begin{itemize}
		\item An increased knowledge of and greater interest in the science, design, development, construction, languages, management and applications of modern computing.
      \item Greater interest in computing and its applications.
      \item A means of communication between persons having an interest in computing
	\end{itemize}
	\item The Chapter will serve students at the University of Kansas at Lawrence and other interested persons in the Lawrence and Eastern Kansas community.
	\item The Chapter is chartered by the ACM.
\end{enumerate}

\section*{Article III: Membership}

The provisions of this section must conform to the membership provisions specified in ACM's Bylaws (Bylaw 5, Section 5; ACM Constitution Article 3).

\begin{enumerate}
	\item Membership in the Student Chapter shall be open to all ACM members and nonmembers.
	\item Voting membership in the Student Chapter shall be granted to all active chapter members.
	\item Membership shall not be restricted according to race, creed, age, gender, disability, nationality, sexual orientation, economic status, veteran status, or parenthood.
\end{enumerate}


\section*{Article IV: Officers}
\begin{enumerate}
	\item The officers of this Chapter shall be: Chair, Vice Chair, and Treasurer. These individuals must be ACM Student Members. In addition, a Faculty Sponsor with an ACM Professional Membership is required. These officers constitute the Council. A minimum of three officers to establish a Chapter. Other officers may also be established.
	\item All required officers of the Chapter must be members of ACM.
	\item The officers shall be elected by a plurality of the votes cast at the annual election meeting. They shall take office on January 1st and serve for one year. [It is highly recommended that the Chapter's election be held at the last meeting in the fall with the new officers taking office in January. This provides for a period of transition from the outgoing Council to the incoming Council as well as providing continuity of management and planning over the summer.]
	\item Appointment or nomination of an individual to an officer positions within ACM shall be in general limited to two full consecutive terms in the same position.  This recommendation is intended to encourage the continuing infusion of new volunteers into the organization and to encourage office holders to give thought to planning for their successor.  Appointment or nomination to a third or subsequent consecutive term should be limited to situations where such appointment or nomination is believed to be in the best interests of the Association.
\end{enumerate}

\section*{Article V: Duties of Officers}
\begin{enumerate}
	\item The Chair is the principal officer and is responsible for leading the Chapter and managing its activities in accordance with the policies and procedures of the ACM and these bylaws. The Chair shall preside at all meetings of the chapter and of its Executive Council. The Executive Council shall consist of the Chapter officers, the Student Chapter Sponsor, and chairs of the Chapter's standing committees.
	\item The Vice Chair shall preside at meetings in the absence of the Chair, assist the Chair in the management of the Chapter, and perform other duties that may be assigned by the Chair.
	\item The Treasurer shall keep the minutes of all Chapter and Executive Council meetings and maintain the chapter's financial records. Other duties include:
		\begin{itemize}
			\item Collecting dues, pay all bill, and maintain records for the chapter
			\item Preparation of the Chapter's annual report and officer contact information, and submission of these to ACM Headquarters via the Chapter Administrative Interface.
			\item Submission of any proposed amendment to these bylaws to the ACM Chief Operating Officer. Proposed amendments must be approved before they can be submitted to the Chapter's membership for a vote.
			\item Perform other duties as assigned by the Chair.
		\end{itemize}
\end{enumerate}

\section*{Article VI: Chapter Sponsor}

The Sponsor shall be a faculty member or full-time staff member of your school. Each Student Chapter has one Sponsor.
\begin{enumerate}
	\item The Student Chapter Sponsor shall be a voting member of ACM and either a member of the faculty or full-time staff of the University of Kansas.
	\item The Student Chapter Sponsor shall be selected by the Executive Council immediately following the Election Meeting. The selection shall be confirmed by the school.
	\item The Student Chapter Sponsor shall be generally responsible for the activities of the Chapter. Specifically, the Sponsor:
    \begin{itemize}
		\item helps provide continuity from year to year as student leadership and personnel change;
		\item promotes good student-faculty relationships;
		\item helps maintain university standards in all activities of the Chapter;
		\item exercises financial supervision, if necessary, by promoting prompt payment of bills and collection of dues, and overseeing the settlement of all accounts in the event of dissolution of the Chapter.
		\item represents the Chapter interests to the faculty and administration.
		\item for high school chapters and underage students, the chapter sponsor must be in attendance at every meeting that is held in the evening. In the event that the appointed sponsor is not available, another faculty member may chaperon the meeting. If both are not available, a local area professional, previously investigated and approved by the school, can be assigned to supervise evening meetings.
	\end{itemize}
\end{enumerate}


\section*{Article VII: Executive Council}

There is no requirement that there be an Executive Council, but if there is one, the Chair would be the presiding officer. If there is no specific Executive Council, the set of officers are the Executive Council.

\begin{enumerate}
	\item The Executive Council shall consist of all the Chapter officers, the Student Chapter Sponsor, a designated representative of each SIG, and a designated representative of each Committee.
	\item The Executive Council meetings shall be open for attendance to any ACM member, unless the meeting is otherwise specified by the Chapter Chair.
	\item The Executive Council shall meet when called by the Chair or when called by a minimum of one-third of the Executive Council membership.
	\item The Executive Council voting rights extend only to those official members of the Executive Council.
	\item Membership in the Executive Council may be revoked from any Executive Council member demonstrating behavior that is a substantial violation of the official ACM Code of Integrity or upon extreme dereliction of duty upon a three-fourths affirmative vote of the Executive Council. The vote must be preceded by a hearing in accordance with the Appeal Process.
	\item Any Executive Council vote must have a Quorum of two-thirds of Executive Council Votes in attendance.
	\item Any Executive Council decision must be agreed upon by a defined percentage of all Executive Council votes in the Quorum.
	\item Unless otherwise specified a decision must be agreed upon by a majority percentage of Executive Council Votes.
\end{enumerate}

\section*{Article VIII: Duties of Executive Council}

\begin{enumerate}
	\item The Executive Council shall plan meetings at least 2 times a year in accordance with the needs of the Chapter. The Chapter shall hold meetings only in places that are open, safe, and accessible. There may be additional local government requirements about openness to the public and accessibility for the handicapped.
	\item The Executive Council shall create working committees in accordance with the needs of the Chapter. These committees may be used to organize events and projects for the Chapter.
	\item The Executive Council shall determine the annual dues for the members of the Chapter.
\end{enumerate}

\section*{Article IX: Meetings}

\begin{enumerate}
	\item The Chapter shall hold meetings only in places that are open and accessible to all members of the Association.
	\item The Annual Election meeting should be held at the last meeting of the semester. At this meeting, the Treasurer each shall present the required reports. Also, the election of officers shall be held. Written notices of all meetings shall be distributed to all members at least one week prior to any meeting.
\end{enumerate}

\section*{Article X: Disbursements and Dues}

\begin{enumerate}
	\item Disbursements from the Treasury for Chapter expenditures shall be made by the Treasurer or Chapter Sponsor with authorization of the Executive Council and shall be included in the minutes of its meetings.
	\item Dues shall be fixed annually by the Executive Council.
\end{enumerate}

\section*{Article XI: Amendment and Voting Procedures}
\begin{enumerate}
	\item All proposed changes to these Chapter Bylaws shall be approved by the ACM Chief Operating Officer before being presented to the Chapter membership for a vote.
	\item No official business of the Chapter shall be conducted unless a quorum is present. A quorum of the Chapter shall be defined as a majority of the voting membership of the Chapter
	\item A simple majority of the voting members present shall be required to carry a motion.
	\item Officers will be elected by a plurality of votes cast.
\end{enumerate}

\section*{Article XII: Code of Conduct}

\begin{enumerate}
	\item Harassment is unwelcome or hostile behavior, including speech that intimidates, creates discomfort, or interferes with a person's participation or opportunity for participation, in a conference, event or program. Harassment in any form, including but not limited to harassment based on alienage or citizenship, age, color, creed, disability, marital status, military status, national origin, pregnancy, childbirth- and pregnancy-related medical conditions, race, religion, sex, gender, veteran status, sexual orientation or any other status protected by laws in which the chapter meeting or chapter event is being held, will not be tolerated. Harassment includes the use of abusive or degrading language, intimidation, stalking, harassing photography or recording, inappropriate physical contact, sexual imagery and unwelcome sexual attention. A response that the participant was "just joking," or "teasing," or being "playful," will not be accepted.
	\item Anyone witnessing or subject to unacceptable behavior should notify a chapter officer or ACM Headquarters.
	\item Individuals violating these standards may be sanctioned or excluded from further participation at the discretion of the chapter officers or responsible committee members.
\end{enumerate}

\section*{Article XIII: Dissolution of the Chapter}

\begin{enumerate}
	\item Dissolution of this Chapter by consent of the members shall consist of unanimous agreement of all its officers together with a majority vote at a meeting which has been publicized in advance to all members of the Chapter for the purpose of taking this vote.
	\item Should this Chapter be dissolved, its assets and liabilities shall be transferred to ACM and shall be supervised by the ACM Finance Director. Funds given to the chapter from the University shall be returned to the University.
\end{enumerate}



\section{SIGs Bylaws}
SIGs must abide by the same ACM bylaws. However, these laws, positions, and responsibilites are seperate from that of ACM@KU. You will elect your own Chair, Vice Chair, and Treasurer. The operations of each SIG are the responsibilities of its officers and not ACM@KU officers.

%======================
