%
% File: chap05.tex
% Author: Wesley Hoffman
% Description: Engineering Student Council
%
\let\textcircled=\pgftextcircled
\chapter{Dealing with ESC}
\label{chap:esc}

\initial{T}he purpose of Engineering Student Council (ESC) is to facilitate communication between the faculty and staff of the University of Kansas School of Engineering and its students, promoting engineering education and involvement within the school, and serving as a collective voice for the engineering student community.

ESC does this by:
\begin{itemize}
	\item Holding bi-weekly meetings with engineering student organization representatives and the School of Engineering administration
	\item Hosting social, professional, and community service events for students of the School of Engineering
	\item Organizing the Funding Advisory Committee to allocate funding to student groups for projects, conferences, and professional events
	\item Representing the School of Engineering students in campus wide events such as Homecoming and other philanthropic events.
\end{itemize}

%======================

\section{Engineering Expo}
\label{sec:sec01}

Engineering Expo is an annual student-organized event held since 1911 to create excitement and interest in the fields of math, science, and engineering. During the three-day event, over 3000 K-12 students, community members, and college students will participate in design competitions, hear from an industry professional about engineering in the real world, and dive into interactive demonstrations.  Each day of Engineering Expo is unique and focuses on a different audience.

ACM@KU has set up programming demos and exercises focused at younger (K - Jr. High) students to inspire an interest in Computing. The Expo is a great time to reach out to the surrounding community and show them what it means to be a student in Computing. The creative and organizational development of our exposition is the responsibility of the Expo Committee (\hyperref[sec:committees]{Section 2.8}).

\subsection*{Thursday \& Friday:}

The Thursday and Friday of Engineering Expo focuses on our K-12 student visitors as well as community members at large. Schools from across the state and from neighboring areas are invited to attend. Beginning the day is an opening session at the Lied Center in which a distinguished keynote speaker will address the importance of Engineering in society. Following the opening session, students will have the opportunity to get out of the classroom and put their math, science, and engineering skills to the test in 11 design competitions catering to all ages. Beyond design competitions, students can view displays and demonstrations of over 25 organizations from all the various disciplines in the School of Engineering, Chemistry, Mathematics and Physics Departments.  Ending the day will be an awards ceremony in which the winners of the various competitions will be announced. Throughout the day, community members are invited to come and experience the open-house at Engineering Expo.
\\
\\
Middle School teams can compete on February 25th, 2016
\\
High School and Elementary School teams can compete on February 26th, 2016

\subsection*{Saturday:}

Saturday of Expo provides community members with the opportunity to see all the research and activities that are currently going on in the School of Engineering. KU Students can also participate in competitions on this day. Demonstrations, activities, and displays for the various organizations will once again be open for viewing by attendees.
\\
\\
College teams can compete on [Add Expo date for your year]

\section{Chapter Involvement in ESC}

Each meeting needs to be attended by the Chapter ESC Rep. ESC is a source of funding and involvement to the University and School of Engineering.

%======================
