%
% File: chap07.tex
% Author: Wesley Hoffman
% Description: SIGs
%
\let\textcircled=\pgftextcircled
\chapter{Special Interest Groups}
\label{chap:SIGs}

\initial{A}CM's Special Interest Groups (SIGs) represent the major areas of the dynamic computing field.  A primary source of original research and personal perspectives from the world's leading thinkers in computing and information technology, they foster technical communities within their respective specialties across countries and continents.

ACM's SIGs are invested in advancing the skills of their members, keeping them abreast of emerging trends. They offer opportunities for networking with colleagues, staying connected to peers and negotiating the strategic challenges of the digital age.

SIGs drive innovation across a broad spectrum of computing disciplines, including programming languages, graphics and interactive techniques, computer-human interaction, data science, mobile communications, artificial intelligence, education, and theory, among many others. They publish newsletters and magazines, encourage excellence through multiple recognition programs, and organize conferences and activities on a local-to-global scale.

\textit{NEVER register a SIG with SILC. NEVER.}

%======================
\section{Formation}
\begin{itemize}
   \item Any group that consists of at least five members may apply to become a Special Interest Group of this Chapter.
   \item There must be at least one member to serve as Chair of the proposed SIG.
   \item The SIG Chair(s) must be an Active Member of ACM@KU.
   \item Each semester the SIG Chair(s) may specify up to one other designated representative to the Executive Council for that semester, who must also be an Active Member of ACM@KU.
   \item A written or electronic application for the formation of a SIG must be presented to the Executive Council.
   \item Upon approval of two-thirds of the Executive Council, the SIG officially becomes an active SIG of this Chapter.
\end{itemize}
\section{Responsibilities}
\begin{itemize}
   \item A SIG of this Chapter must hold meetings at least once per month during the Spring and Fall Semesters.
   \item A SIG of this Chapter must have a designated representative present at each Executive Council meeting.
\end{itemize}
\section{Privileges}
\begin{itemize}
   \item A SIG of this Chapter will be allowed to use Chapter office space for its meetings and projects with approval of the Executive Council.
   \item A SIG of this Chapter will be able to use the ACM@KU name in promotion of that SIG or its events.
   \item A SIG will be provided a mailbox in the ACM office for SIG related correspondence. (Does ACM@KU have a mailbox?)
   \item A SIG of this Chapter is allowed to submit funding requests to the Executive Council.
\end{itemize}
\section{Removal}
\begin{itemize}
   \item If a SIG of this Chapter does not adhere to these responsibilities, it may be removed from ACM by a two-thirds vote of the Executive Council.
   \item If at any point a SIG does not have a Chair the SIG is automatically removed from ACM.
   \item Resources owned by a removed SIG will be transferred to ACM@KU and may be reallocated by an Executive Council Vote.
\end{itemize}


\section{Active SIGs}

\subsection{Programming Club}
As of January 2016, programming club is being developed as an official ACM@KU SIG so it is currently ran by two Co-Chairs.

%======================
