%
% File: chap01.tex
% Author: Wesley Hoffman
% Description: Introduction and Welcome
%
\let\textcircled=\pgftextcircled
\chapter{Introduction}
\label{chap:intro}

\initial{W}elcome to the first edition of the KU ACM Student Chapter Officer's Handbook. This will be your guide on how to best run the ACM Student Chapter and ensure its success for now and the years ahead. This handbook is to be passed down to each new group of officers and can be edited and revised as seen fit. However, this should not apply to official parent organization guidelines, governance, and bylaws. Currently, this chapter has a short history, but it is built of very proud and passionate individuals. Hopefully, these tidbits on the lessons and rules we learned will help you avoid and learn from our mistakes.

%=======
\section{Name}
\label{sec:sec01}

This organization shall be called the University of Kansas at Lawrence Student Chapter of the Association for Computing Machinery herein referred to as ACM@KU. All affiliated Special Interest Groups are herein referred to as SIGs.
This organization may officially be referred to by any of the following terms:
\begin{itemize}
	\item University of Kansas at Lawrence Student Chapter of the Association for Computing Machinery
	\item Association for Computing Machinery at Lawrence
	\item ACM@KU
\end{itemize}

\section{Introduction to Being an Officer}
\label{sec:sec02}

Each officer is to be responsible for their duties outlined in the following subsections. Clear communication between one another invokes a good understanding. If for any reason an officer cannot fulfill their duties, other officers may be delegated to support them until said officer can resume their responsibilities. Additional officer positions may be added or removed as need be, including SIG leaders, event coordinators, et cetera.  However, the core officer group must be present, as dictated by the ACM and SILC. These are not removable positions.
\begin{itemize}
	\item ACM@KU shall have four official positions to represent the organization: Chair, Vice Chair, Treasurer, and Secretary.
	\item The officers will be elected each March (maybe moving to December) in a specially designated election meeting chosen and publicized in good faith by the Executive Council and run by the Chair or by his or her appointed representative.
	\item No officer may hold more than one office in ACM@KU simultaneously.
	\item All required officers must, upon election, become members of Association for Computing Machinery International.
\end{itemize}

\subsection{Core Officers}
\label{subsec:subsec01}

\begin{itemize}
	\item Chair
   \item Vice Chair
   \item Secretary
   \item Treasurer
   \item Faculty Sponsor
\end{itemize}

\subsection{Additional Officers}
\label{subsec:subsec02}

\begin{itemize}
	\item Engineering Student Council Representative
   \item Publicity Director
   \item Programming Club Chair
   \item Web Master
\end{itemize}

%=========================================================
